Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-19 paper/paper.tex
Add some other information to the building the data set section of the report

\section{Introduction}

@@

Once the Bolt DB instance is completely populated with all the tickets we were interested in, the analyze command first 
fetches all the issues in the database. Then, it runs in parallel the \emph{seven types of analysis}:
\begin{itemize}
  \item \emph{attachments} - checks whether attachments influence Time-To-Close and also look at what types 
  of attachments (e.g. screenshots, archive, code snippets) influence quality the most;
  \item \emph{steps to reproduce} - performs a complex regex to detect steps to reproduce and then checks whether their presence
  influence the quality of a ticket;
  \item \emph{stack traces} - runs complex regex for detecting stack traces in either summary, description or comments 
  and verifies whether their presence influence Time-To-Close for the ticket;
  \item \emph{comments complexity} - loops through all comments and counts all words; then, the tool verifies whether 
  having many words or comments decreases or increases Time-To-Close for the ticket;
  \item \emph{fields complexity} - same analysis as comments complexity, but only for summary and description;
  \item \emph{grammar correctness} - it uses Azure Cloud Bing Spell Check API \cite{bing} to perform analysis on summary, 
  description and comments; after concatenating everything and making it compatible with the API allowed formats, the tool 
  receives back in the JSON payload not only the number of flagged tokens (i.e. grammar errors), but also their types 
  (e.g. unknown token, misspell);
  \item \emph{sentiment} - uses Google Cloud Platform's Natural Language Processing API \cite{gcp_nlp} to retrieve the 
  sentiment score for summary, description and comments; it first concatenates everything and makes it conform to Google's 
  API and then sends the request, receiving a score from -1 to 1 inclusive (-1 means most negative, 1 means most 
  positive);
\end{itemize}

We hit several issues when working with Google Cloud Platform and Bing Spell

Implementation wise, the application first checks Bolt for tickets and gets either all of them in memory (easier to parse, 
but heavy on resource utilization) or slices them into smaller arrays to get processed afterwards (harder to parse as it 
eventually requires re-creation of the whole array of tickets before inserting back into the database, but it is much 
lighter on computing power). After having the tickets available, we start looping through them and perform all 
analysis types mentioned above. Once some sort of value is computed (e.g. grammar correctness score), it gets set in 
its corresponding field in the ticket struct and subsequently is stored back in the database. We chose this approach because 
we do not want to run the analysis every time we want to plot correlations between variables, but rather have the data 
already available there. Moreover, for external analysis such as hitting Google Cloud Platform APIs, there are costs for 
running the analysis, thus in this way we drastically reduce overall costs for the project.

>>>>

\section{Introduction}\label{intro}

@@

Once the Bolt DB instance is completely populated with all the tickets we were interested in, the analyze command first 
fetches all the issues in the database. The next step is to filter out the tickets based on the following criteria:
\begin{itemize}
  \item tickets are \emph{High Priority} - the ticket status was marked either Blocker, Critical, Major or High;
  \item tickets were closed and had a maximum \emph{Time-To-Close} value of 27,000 hours (roughly 3 years) (we added the 
  higher bound as well in order to eliminate outliers produced by wrong data retrieved by Jira);
  \item remove outliers for all categories - some fields for a small number of tickets that had wrong values (e.g. one ticket
  had over 270,000 comments) introduced by the team behind the project and we needed to exclude them so that the analysis 
  produced correct results.
\end{itemize}

Then, it runs in parallel the \emph{seven types of analysis} for answering the research questions outlied in Section \ref{intro}, 
each in its own separate goroutine in order to speed up the process:
\begin{itemize}
  \item \emph{attachments} - checks whether attachments influence Time-To-Close and also look at what types 
  of attachments (e.g. screenshots, archive, code snippets) influence quality the most;
  \item \emph{steps to reproduce} - performs a complex regex to detect steps to reproduce and then checks whether their presence
  influence the quality of a ticket;
  \item \emph{stack traces} - runs complex regex for detecting exception stack traces in either summary, description or comments 
  and verifies whether their presence influence Time-To-Close for the ticket; this analysis only inspects projects
  written in Java as it is the most popular proponent built-in of stack traces;
  \item \emph{comments complexity} - loops through all comments and counts all words; then, the tool verifies whether 
  the number of words in comments has an impact on the Time-To-Close for the ticket;
  \item \emph{fields complexity} - same analysis as comments complexity, but only for summary and description wordiness;
  \item \emph{grammar correctness} - it uses Azure Cloud Bing Spell Check API \cite{bing} to perform analysis on summary, 
  description and comments; after concatenating everything and making it compatible with the API allowed formats, the tool 
  receives back in the JSON payload not only the number of flagged tokens (i.e. grammar errors), but also their types 
  (e.g. unknown token, misspell);
  \item \emph{sentiment} - uses Google Cloud Platform's Natural Language Processing API \cite{gcp_nlp} to retrieve the 
  sentiment score for summary, description and comments; it first concatenates everything and makes it conform to Google's 
  API and then sends the request, receiving a score from -1 to 1 inclusive (-1 means most negative, 1 means most 
  positive);
\end{itemize}

We needed to be extra cautious when working with Google Cloud Platform and Bing Spell Check APIs, especially 
regarding rate limiting. Google's NLP APIs have a maximum rate of 10 requests per second, while Microsoft APIs 
have a maximum rate of  100 requests per second, thus we needed to conform to their guidelines and restrict our 
application to send more than allowed, otherwise our IP addresses could have been blacklisted. We also did not want 
to exceed our free trial credits, therefore we calculated in advance how many requests we had available and computed 
scores only for those tickets.

The application first checks Bolt for tickets and gets either all of them in memory (easier to parse, 
but heavy on resource utilization) or slices them into smaller arrays to get processed afterwards (harder to parse as it 
eventually requires re-creation of the whole array of tickets before inserting back into the database, but it is much 
lighter on computing power). After having the tickets available, we start looping through them and perform all 
analysis types mentioned above. Once some sort of value is computed (e.g. grammar correctness score), it gets set in 
its corresponding field in the ticket struct and is subsequently stored back in the database. We chose this approach because 
we do not want to run the analysis every time we want to plot correlations between variables, but rather have the data 
already available there. Moreover, for analysis depending on third party services such as the Google Cloud Platform 
Natural Processing Language API, we would incur costs, thus having everything saved in the database and running the 
analysis only if the value has not been already computed allowed us to investigate the tickets without exceeding the 
free trial credits.
